IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-18 ms.tex
I added a few more tables and sentences about the observations.

\section{Introduction}
\citep{burgaser2014irtf}.

@@

\section{Observations}

@@

\section{Acknowledgements}

%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

>>>>

\section{Introduction}
\citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.

@@

\input{bd_table.tex}

\section{Observations}
We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.

\input{observing_table.tex}

We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.

@@

\section{Acknowledgements}
%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.
